msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-09 paper.tex
Changes to data interchange section. Added some ABC references.

\subsection*{Data interchange and interoperability}
The point of simulations is to generate data and the efficiency with
which simulated data can be incorporated into an overall application
is an important---if often overlooked---issue.
For example, Approximate Bayesian Computation
(ABC)~\citep{beaumont2002approximate,csillery2010approximate}
and more recent machine learning
methods~\citep{sheehan2016deep,schrider2018supervised,flagel2019unreasonable}
perform population genetic inference by using large numbers of
simulations as training data. Clearly, simulation efficiency is
crucial since the size and number of simulations that can be performed
largely determines the scope of what can be inferred. Equally important,
however, is the efficiency with which the simulation results can be
transformed into the specific input required by the inference method.
In the case of ABC, this is usually a set of summary statistics of the
sequence data. General approaches such as
ABCtoolbox~\citep{wegmann2010abctoolbox} connect to
simulation and summary statistic computation programs via text streams
and are quite flexible, but the overhead involved in processing
the text is often a computational bottleneck.
Other methods such as DIYABC~\citep{cornuet2008inferring}
or PopABC~\citep{lopes2009popabc} avoid this bottleneck by
developing their own specialised simulators, tightly integrating them
with the inference method. While this is certainly more efficient,
there is a great deal of duplication of effort and significant
room for error.

@@

\item Side note somewhere: with efficient access to branch length
    statisics~\citep{ralph2019efficiently}, maybe we don't need to
    simulate mutations at all.

>>>>

\subsection*{Data interchange and interoperability}
The point of simulations is to generate data and the efficiency with
which simulated data can be incorporated into an overall application
is an important---if often overlooked---issue.
For example, Approximate Bayesian Computation
(ABC)~\citep{beaumont2002approximate,csillery2010approximate}
and more recent machine learning
methods~\citep{sheehan2016deep,schrider2018supervised,flagel2019unreasonable}
perform population genetic inference by using large numbers of
simulations as training data. Clearly, simulation efficiency is
crucial since the size and number of simulations that can be performed determines
the depth to which the model and parameter space can be sampled from.
Equally important,
however, is the efficiency with which the simulation results can be
transformed into the specific input required by the inference method.
In the case of ABC, this is usually a set of summary statistics of the sequence data.
Modern approaches such as
ABC-RF~\citep{raynal2019abc,pudlo2016abc} and
ABC-NN~\citep{csillery2012abc,blum2010abc} can accommodate large numbers of statistics
that are individually weakly informative, but jointly close to sufficient for the 
desired model or parameter.
However, the computational resources needed to calculate these statistics can be even 
greater than those used to generate the simulated datasets.
[An example would be good here? Hmmm...]

General approaches such as
ABCtoolbox~\citep{wegmann2010abctoolbox} connect to
simulation and summary statistic computation programs via text streams
and are quite flexible, but the overhead involved in processing
the text is often a computational bottleneck.
Other methods such as DIYABC~\citep{cornuet2008inferring}
or PopABC~\citep{lopes2009popabc} avoid this bottleneck by
developing their own specialised simulators, tightly integrating them
with the inference method. While this is certainly more efficient,
there is a great deal of duplication of effort and significant
room for error.

@@

\item Side note somewhere: with efficient access to branch length
    statistics~\citep{ralph2019efficiently}, maybe we don't need to
    simulate mutations at all.
[GT: I'm not so sure about this -- the desired statistics/summaries 
must be calculated on the observed dataset as well as on the many
simulated datasets.
Unless the observed dataset is stored as a tree sequence,
(because it has been through tsinfer, for example),
it's not clear how branch or node stats could be calculated 
from it.
]
